`r title`

### 2021-03-04 lib/report.Rmd
progress
report and integration tools

\begin{center}
2010 Census population: `r comma_num(population)`

@@

@@

@@

>>>>

\begin{center}
2017 5 year ACS population estimate: `r comma_num(population)`

@@

```{r geocoding_tbl, fig.align = 'left'}
display_if_exists("geocoding_tbl")
```

@@

Google Maps Geocoding Cost CDF

Interpretation: we can get X% of the stops by geocoding half the locations (so half the cost) and we can get X% of stops by geocoding 75% of the locations (so .75 of the cost). Replace X with the relevant y-intercepts.

```{r geocoded_cdf, fig.height = 10}
display_if_exists("geocoded_cdf")
display_if_exists("geocoding_tbl_fractional")
```

@@

```{r correct_predicates_table}
correct_predicates_table
```
